Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Fix grammar error in paper
Make small tweaks to wording around notation

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive, bounded, and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

We reestimate the ATE on health and schooling with robust procedures. To be
specific, we apply both the robust procedure proposed by CCT and the bootstrap
procedure introduced in this paper.  Our bootstrap estimator uses the
AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
bootstrap from \citet{DF08}. In the bootstrap
procedure, we use 500 bootstraps for bias correction and 999 to calculate the
confidence intervals. The analytical estimator using CCT's bias correction and variance estimator use
their AMSE-optimal bandwidths as well.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

@@

For reference, define the variance terms
\begin{equation}\label{eq:8}
  V(h)
  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
    \Gamma_{-,1}(h)^{-1}
  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
\end{equation}
and
\begin{multline}\label{eq:13}
  C(h,b) =
  \tfrac{1}{n} \, e_2' \big[
    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
  \big] e_2 \\
  - \tfrac{2 h^2}{n b^{2}}
    e_0' \Big[
    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
    \Big] e_2.
\end{multline}
See CCT for more on the motivation and derivation of these formulas.

@@

To prove convergence in probability of the bootstrap variance, note that the
wild bootstrap ensures
\begin{equation*}
  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
\end{equation*}
for any measurable function $R(\cdot)$.
Given this expression for the iterated bootstrap and the formula for the
variance conditional on $X$ presented at the end of the introduction to this
appendix, it suffices to show that
\begin{gather}
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
  \label{eq:3} \\
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
  + o_p(\tfrac{1}{b^2})
  \label{eq:5} \\
  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
  \label{eq:7}
\end{gather}
But these convergence results follow from CCT's results on
$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
and standard arguments on the convergence of residuals to
the population error term.

>>>>

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive, bounded, and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
\end{assumption}
To simplify notation, define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

We reestimate the ATE on health and schooling with robust procedures. To be
specific, we apply both the robust procedure proposed by CCT and the bootstrap
procedure introduced in this paper.  Our bootstrap estimator uses the
AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
bootstrap from \citet{DF08}. In the bootstrap
procedure, we use 500 bootstraps for bias correction and 999 to calculate the
confidence intervals. The analytical estimator using CCT's bias correction and
variance estimator uses
their AMSE-optimal bandwidths as well.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else and assume, with some abuse of notation, that the
dimension of $e_p$ adapts to make matrix and vector operations
conformable. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
with $m = \min(h,b)$.
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

@@

Finally, define the variance components
\begin{equation}\label{eq:8}
  V(h)
  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
    \Gamma_{-,1}(h)^{-1}
  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
\end{equation}
and
\begin{multline}\label{eq:13}
  C(h,b) =
  \tfrac{1}{n} \, e_2' \big[
    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
  \big] e_2 \\
  - \tfrac{2 h^2}{n b^{2}}
    e_0' \Big[
    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
    \Big] e_2.
\end{multline}
See CCT for more on the motivation and derivation of these formulas.

@@

To prove convergence in probability of the bootstrap variance, note that the
wild bootstrap ensures
\begin{equation*}
  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
\end{equation*}
for any measurable function $R(\cdot)$.
Given this expression for the iterated bootstrap and the formula for the
variance conditional on $X$ presented at the end of the introduction to the
appendix, it suffices to show that
\begin{gather}
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
  \label{eq:3} \\
  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
  + o_p(\tfrac{1}{b^2})
  \label{eq:5} \\
  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
  \label{eq:7}
\end{gather}
But these convergence results follow from CCT's results on
$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
and standard arguments on the convergence of residuals to
the population error term.
